Nanophotonic Computational Design

### 2013-02-24 defense/pres3.tex
Getting there...

@@

\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause

\let\thefootnote\relax\footnotetext{Footnotetext without footnote mark} 
\I  Result\footnote{Lu et al, Optics Express (2010)}: 
    Perfect performance, but unmanufacturable structure ($z$)
\nextpage

@@

\bigfig{1d_regularized_12}
\I  Unfortunately, regularization on $z$ decreases performance 
\nextpage

\smallfig{1d_regularized_3}
    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
\I  Decreased performance a result of non-zero physics residual at optimum
\nextpage

@@

\smallfig{1d_alternate}
\I  Iterative strategy produces $z$ (structure) that 
    \BI is better behaved
    \I  more accurately produces $x$ \EI
\nextpage

@@

\smallfig{1d_hardlimit}
\I  Well-behaved, manufacturable $z$ (structure)
\I  Final $x$ (field) accurately reproduced
\I  Majority of elements of $z$ are fortuitously at one limit or the other!
\nextpage

\I  Can be used to create 2D resonators
\smallfig{2d_circ}
\nextpage

\I  3D resonators can be designed using a ``2.5D'' approximation
\smallfig{25d_circ}
\nextpage

@@

\I  Applied to the design of 2D waveguide mode couplers
\smallfig{ob1_explanation}
\I  Produced designs which exhibited
    \BI High efficiency ($\sim 98\%$)
    \I  Small device footprints ($1.5-4$ square vacuum wavelengths) \EI
\nextpage

\I  Coupler to wide, low-index waveguide
\medfig{ob1_wg}
\nextpage

\I  Coupler from fundamental to second-order waveguide mode
\medfig{ob1_wg2}
\nextpage

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\nextpage

\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
    \BI Millions of variables
    \I  Famously ill-conditioned 
    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
\pause
\smallfig{wonseok}
\I  Fortunately, Wonseok had already solved this problem

>>>>

% No mark footnotes.
\let\thefootnote\relax

@@

\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause
\I  Result: Perfect performance, but unmanufacturable structure ($z$)
\nextpage

@@

\myfig{1d_regularized_12}{11.5}
\I  Unfortunately, regularization on $z$ decreases performance 
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\smallfig{1d_regularized_3}
    \BE \minimize_z \|A(z)x - b\|^2 + \eta\|z-z_0\|^2 \EE
\I  Decreased performance a result of non-zero physics residual at optimum
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\smallfig{1d_alternate}
\I  Iterative strategy produces $z$ (structure) that 
    \BI is better behaved
    \I  more accurately produces $x$ \EI
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\smallfig{1d_hardlimit}
\I  Well-behaved, manufacturable $z$ (structure)
\I  Final $x$ (field) accurately reproduced
\I  Majority of elements of $z$ are fortuitously at one limit or the other!
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  Can be used to create 2D resonators
\smallfig{2d_circ}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  3D resonators can be designed using a ``2.5D'' approximation
\smallfig{25d_circ}
\footnotetext{J. Lu, S. Boyd, J. Vuckovic, Optics Express (2011)}
\nextpage

@@

\I  Applied to the design of 2D waveguide mode couplers
\smallfig{ob1_explanation}
\I  Produced designs which exhibited
    \BI High efficiency ($\sim 98\%$)
    \I  Small device footprints ($1.5-4$ square vacuum wavelengths) \EI
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\I  Coupler to wide, low-index waveguide
\medfig{ob1_wg}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\I  Coupler from fundamental to second-order waveguide mode
\medfig{ob1_wg2}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
    Optics Express (2012)}
\nextpage

\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
    \BI Millions of variables
    \I  Famously ill-conditioned 
    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
\pause
\smallfig{wonseok}
\I  Fortunately, Wonseok had already solved this problem
\footnotetext{W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,'' J. Comp. Phys. (2012)}
